Turbulence in giant HII regions

### 2021-04-02 mnras_template.tex
Javier edits up to April 2

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Turbulence in GEHRs]{Turbulence in giant extragalactic HII regions}

@@

We used the radial velocity field in H$\alpha$ emission with the aim of characterizing the turbulent state of the ionized gas in giant HII regions. For this purpose we use long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample was investigated applying the second order structure function. The correlations in our results are evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

Different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}. Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS). The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} is related to the existence of turbulent flows. Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.

The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}. Their aim was to investigate the projection of a three-dimensional function into the plane of the sky. This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula. The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}. In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region. Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

@@

\citet{smith1970} discovered that the line width of GEHRs was supersonic, of the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). Correlations between kinematics and physical properties of GEHR have been common tools to study this excess. They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

Our objective is to characterize the turbulent regime for different ions in different GEHRs. We compare our results with previous investigations.

@@

The archival data used in this work was obtained with the ISIS spectrograph and the TAURUS-II Fabry Perot in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.

@@

Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$. ISIS observations have been limited with the aim to match the zone cover by TAURUS instrument. The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a  reference point the most luminous pixel. This pixels has a value of -253.11 km/s. Figure \ref{fig:M595} and \ref{fig:MHub} shows the two-dimensional radial velocity map in H$\alpha$ of NGC 595, Hubble V and Hubble X, respectively.

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/6ISIS.png}
\includegraphics[width=2.5in]{Figures/6TAU.png}
\caption{Radial velocity maps of NGC 604 in H$\alpha$. Above: ISIS observations. Below: TAURUS observations. }
\label{fig:M604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/5TAU.png}
\caption{Radial velocity maps of NGC 595 in H$\alpha$.}
\label{fig:M595}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Turbulence}\label{sec:turb}

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow, where an energy cascade is taking place. The energy cascades goes downward, from the largest vortices until it reaches dissipation with the smallest vortices. 
In this energy cascade three scales can be defined: the energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two. The energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).

If we consider the mean specific energy transfer, $\langle \epsilon \rangle$, the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations. Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$ and is the energy integral above the associated $k$, defined as:

Considering that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:

@@

as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory. In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation. If we consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:

@@

@@

Figure \ref{fig:SF604} shows the structure function (Equation \ref{eq:S}) of NGC 604 for the H$\alpha$ emission line for the ISIS and TAURUS instruments. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument 7.3 km/s. The fit to the power-law of the structure function is performed over the scales of 4 to 11 pc. The structure functions keep going up to scales of 70 pc, above these value the structure function falls steeply for the ISIS. As \cite{arthur2016turbulence} mentioned, the more pronounced steeping for small scales, below 4 pc in our case, is due to the spatial resolution of the observations. In comparison with TAURUS, ISIS values are higher but are able to maintain the form of the structure function.

Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ is 6.6 km/s. In this case it is possible to fit values under 4 pc, but this small scale region is affected due to the seeing. The range of scale for this regions stays between 10 and 11 pc as in NGC 604. The values of the structure function rise until 30 pc. Scales larger than this shows a random pattern around 2$\sigma$.

Figure \ref{fig:SFV} shows the structure function of Hubble V for the H$\alpha$ emission line. The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s. The structure function values keep going up and reach a maximum at $\sim$28 pc, above this value there is no clear pattern.

@@

\begin{table}
\begin{center}\caption{Main results.}
\begin{tabular}{cccccc}\hline
Region   & L$_{c}$  & m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{c}$/l$_{0}$ \\\hline
NGC 604 & 178  &     1.7   &     11       &    7.3        & 16 	\\
NGC 595 & 200  &     1.7   &     11      &    6.6        & 18 	\\
Hubble V & 90  &     1.8   &     3       &    2.8      & 30 	\\
Hubble X & 100  &     1.7   &     5       &    3.6      & 20 	\\
\end{tabular}\label{tab:Res}
\end{center}
\end{table}

\begin{figure}
\centering 
\includegraphics[width=3.5in]{Figures/SF604.pdf}
\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments. The figure also shows the structure functions presented in previous works.}
\label{fig:SF604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=4in]{Figures/SF595.pdf}
\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument. The figure also shows the structure functions presented in previous works.}
\label{fig:SF595}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/HV}
\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFV}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/HX}
\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFX}
\end{figure}

@@

In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$. Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the largest scales of 150 pc. Therefore this periodic behavior is related to scales of $\sim$100 pc across our sample box.

Figure \ref{fig:SF604} shows similarity in the TAURUS results and previous works \citep{tanco1997,2019arXiv191203543M}. The agreement lies that observations are the same but the procedure of calculating the structure function is different. \citep{2019arXiv191203543M} has $\sigma$ of 7.2 while we have 7.3 km/s. We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results; \citep{tanco1997} also show this periodic pattern at large scales.

@@

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Turbulence in GHRs]{Turbulence in giant HII regions}

@@

We used the radial velocity field in H$\alpha$ emission with the aim of characterizing the turbulent state of the ionized gas in giant HII regions. For this purpose we use long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample was investigated applying the second order structure function. The correlations in our results are evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 and a correlation length of 11 pc. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

@@

Different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}. Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS). The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} are related to the existence of turbulent flows. Despite numerous attempts in characterizing the turbulence in the photoionized gas, little is understood on the nature of the problem.

The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}. Their aim was to investigate the projection of a three-dimensional function into the plane of the sky. This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula. The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}. In more recent years \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region. Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

@@

\citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). Correlations between kinematics and physical properties of GEHR have been common tools to study this excess. They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

NGC 604 is the brigthest giant HII region of M33 galaxy, located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc. It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}. \cite{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region. The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein). Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population. \citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).  The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}. This suggest that two episodes of star formation, at least, have taken place in the GEHR.

NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc. The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}. \cite{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$. \cite{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \cite{1993AJ....105.1400D}. It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX). HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}. HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}. Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX. HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

Our objective is to characterize the turbulent regime in different GEHRs. We compare our results with previous investigations.

\subsection{Turbulence}\label{sec:turb}

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place. The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices. 
In the energy cascade three scales are defined based on their Reynolds number. The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale ($L_{I}$) between the previous two. Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k^{-\beta}$ where $k$ is the wave number for a scale $l$ ($k \equiv l^{-1}$).

We can consider that  the mean specific energy transfer, $\langle \epsilon \rangle$, in the inertial range can be denoted as $\epsilon \sim \frac{v_{l}^{2}}{\tau_{l}}$, where $v_{l}^{2}$ is the kinetic energy per mass unit and $\tau_{l}$ the time related with velocity fluctuations. Since the total specific energy of a determined $l$ scale is of the order $\langle v_{l}^{2} \rangle$, the energy integral above the associated $k$, defined as:

Following that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can substitute in equation \ref{eq:veles} and obtain the Kolmogorov law:

@@

The archival data used in this work was obtained with the long-slit ISIS and the Fabry Perot TAURUS-II instruments in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.

@@

Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$. ISIS observations (above) have been limited with the aim to match the zone covered by TAURUS instrument. The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a reference point the most luminous pixel. This pixels has a value of -253.11 km/s. Figure \ref{fig:M595} and \ref{fig:MHub} shows the two-dimensional radial velocity map in H$\alpha$ of NGC 595, Hubble V and Hubble X, respectively.

\subsection{The second order structure function}

@@

as a statistical tool to investigate the relation between a velocity field and the presence of turbulent motions following the Kolmogorov theory. In equation \ref{eq:S}, $V_{r}(\boldsymbol{x})= V_{obs}(\boldsymbol{x})-\langle V_{obs}(\boldsymbol{x}) \rangle$ and N($\boldsymbol{l}$) the number of points at each separation.

We can consider the quadratic velocities differences proportional to the left term in equation \ref{eq:kolm}:

@@

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/6ISIS.png}
\includegraphics[width=2.5in]{Figures/M6T}
\caption{Radial velocity maps of NGC 604 in H$\alpha$. Above: ISIS observations. Below: TAURUS observations. }
\label{fig:M604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/M5T.png}
\caption{Radial velocity maps of NGC 595 in H$\alpha$.}
\label{fig:M595}
\end{figure}

@@

Table \ref{tab:Res} shows the parameters we use to analyze our results. These are, the parameters obtained with a power-law fit of the structure function the index, m$_{2D}$, and the correlation length, l$_{0}$ and the ratio L$_{b}$/l$_{0}$, where L$_{b}$ is the horizontal size in pc of our sample box.

Figure \ref{fig:SF604} shows the structure function (Equation \ref{eq:S}) of NGC 604 for the H$\alpha$ emission line for the ISIS and TAURUS instruments. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ for the ISIS instrument is 8.4 km/s and for TAURUS instrument is 7.3 km/s. The fit to the power-law of the structure function is performed over the scales of 4 to 11 pc. The structure functions keep going up to scales of 70 pc, above these value the structure function falls steeply for the ISIS. As \cite{arthur2016turbulence} mentioned, the more pronounced steeping for small scales, below 4 pc in our case, is due to the spatial resolution of the observations. In comparison with TAURUS values, ISIS values are higher but are able to maintain the form of the structure function.

Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ is 6.6 km/s. The values of the structure function rise until 30 pc.

Figure \ref{fig:SFV} shows the structure function of Hubble V for the H$\alpha$ emission line. The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s. The structure function values keep going up and reach a maximum at $\sim$28 pc.

@@

\begin{table}
\begin{center}\caption{Main results.}
\begin{tabular}{cccccc}\hline
Region   &  m$_{2D}$  & l$_{0}$ [pc] & $\sigma$ [km/s] & L$_{b}$ [pc]  & L$_{b}$/l$_{0}$ \\\hline
NGC 604 &     1.7   &     11       &    7.3         & 170  &  15.4 	\\
NGC 595 &      1.7   &     11      &    6.6        & 200  & 18.1 \\
Hubble V &   1.8   &     3       &    2.8      & 68  &     22.6  	\\
Hubble X &     1.7   &     5       &    3.6      & 61  &  12.2 	\\
\end{tabular}\label{tab:Res}
\end{center}
\end{table}

\begin{figure}
\centering 
\includegraphics[width=3.5in]{Figures/SF604.pdf}
\caption{NGC 604 second-order structure functions for H$\alpha$ emission line for ISIS and TAURUS instruments. The figure also shows the structure functions presented in previous works. The green area represents the scales affected by observational seeing. The vertical line indicate the value of he correlation length. The horizontal line denote the value of $\sigma$.}
\label{fig:SF604}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=4in]{Figures/SF595.pdf}
\caption{NGC 595 second-order structure functions for H$\alpha$ emission line for TAURUS instrument. The figure also shows the structure functions presented in previous works. Same information as Figure \ref{fig:SF604}.}
\label{fig:SF595}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/SFHV}
\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFV}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/SFHX}
\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFX}
\end{figure}

@@

In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions for NGC 604, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$. Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the largest scales of 150 pc. Therefore this periodic behavior is related to scales of $\sim$100 pc across our sample box.

For NGC 595, above 30 pc a random pattern is around 2$\sigma$. Also, we can see this behavior for Hubble V, above 28 pc and Hubble X above 18 pc.

Figure \ref{fig:SF604} shows similarity in the TAURUS results and previous works \citep{tanco1997,2019arXiv191203543M}. The agreement lies that observations are the same but the procedure of calculating the structure function is different. \citep{2019arXiv191203543M} has $\sigma$ of 7.2 while we have 7.3 km/s. We note that our structure function results are more similar to \cite{2019arXiv191203543M} but the periodic behavior is strongly reduced on their results. \citep{tanco1997} also show this periodic pattern at large scales.

@@

\begin{enumerate}
    \item The giant HII regions in  M 33, NGC 604 and NGC 595 shows the same index and correlation lengths of 1.7 and 11 pc. These despite the noted differences on their physical properties and stellar populations. For NGC 604 wee find agreement in the structure function results between our data and previous publications. For NGC 595 our results are different from previous structure functions.

    \item Structure functions are presented for the first time for Hubble X and Hubble V, in NGC 6822. Hubble V shows and index of 1.8 and a correlation length of 4 pc, while Hubble X results are 1.7 and 5 pc.

\end{enumerate}
